Rapid Georectification of Pushbroom Hyperspectral Imagery for Real Time Processing by an Autonomous Aerial Vehicle

### 2023-09-04 paper/paper.tex

%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, inputenc, calc, indentfirst, fancyhdr, graphicx, epstopdf, lastpage, ifthen, float, amsmath, amssymb, lineno, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, tabto, xcolor, colortbl, soul, multirow, microtype, tikz, totcount, changepage, attrib, upgreek, array, tabularx, pbox, ragged2e, tocloft, marginnote, marginfix, enotez, amsthm, natbib, hyperref, cleveref, scrextend, url, geometry, newfloat, caption, draftwatermark, seqsplit
% cleveref: load \crefname definitions after \begin{document}

%=================================================================
% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition, Notation, Assumption
%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=10.5cm]{./assets/radiance.eps}
    \caption{Radiance spectrum captured for single HSI pixel.}
    \label{fig:radiance}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=10.5cm]{./assets/solar_irradiance.eps}
    \caption{Solar Irradiance spectrum captured by downwelling spectrometer.}
    \label{fig:solar-irradiance}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=10.5cm]{./assets/reflectance_rainbow.eps}
    \caption{Resuliting reflectance spectrum.}
    \label{fig:reflectance}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=10.5cm]{./figures/demo-rectified-cube.png}
    \caption{Georectified Hyperspectral Datacube}
    \label{fig:rectified-cube}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}

@@

>>>>

%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, inputenc, calc, indentfirst, fancyhdr, graphicx, epstopdf, lastpage, ifthen, float, amsmath, amssymb, lineno, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, tabto, xcolor, colortbl, soul, multirow, microtype, tikz, totcount, changepage, attrib, upgreek, array, tabularx, pbox, ragged2e, tocloft, marginnote, marginfix, enotez, amsthm, natbib, hyperref, cleveref, scrextend, url, geometry, newfloat, caption, draftwatermark, seqsplit
% cleveref: load \crefname definitions after \begin{document}
%=================================================================
% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition, Notation, Assumption
%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).

@@

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=10.5cm]{./figures/annotated-hsi.eps}
    \caption{Radiance spectrum captured for single HSI pixel.}
    \label{fig:pipeline}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=10.5cm]{./figures/pipeline-figure.eps}
    \caption{Solar Irradiance spectrum captured by downwelling spectrometer.}
    \label{fig:annotated-hsi}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}

@@

- Incorporation of drone into autonomous robotic team
- Long range wireless network (ubiquiti) for data downlink
- Incorporation of edge-ML for direct determination of chemical concentration
- Utility for navigation, waste removal, etc...

Discuss drawbacks (striping in images)
